Delone lattice studies in \CIII, the space of three complex variables

### 2023-02-16 C3/C3.tex
Updating text of article C3 uv5016, "Measuring Lattices: adding file for replies to referees.

	\keyword{Delaunay}
	\keyword{Delone}
	\keyword{Selling}
	\keyword{\CIII}

@@

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932} (see~\citeasnoun{andrews2019a}).
	As a mnemonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).

@@

	\begin{table}	
		\label{tab:operators}
		\begin{tabular}{c l l l }
			\toprule
			Operator			&Usage						&Result					&Name\\
			\midrule
			$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
			$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
			$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
			$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
			$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
			$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\
			\bottomrule
		\end{tabular}		
	\end{table}

@@

	$\begin{bmatrix}
		\Minus{}_r		& 0					& 0 \\
		\Plus{}_r		&  \textrm{i}\Re{}	& \Re{} \\
		\textfrak{P}_r	& \textrm{i}\Im{}	& \Im{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0 				& 0 \\
		\Plus{}_r	&\textrm{i}\Im{}	& \Im{} \\
		\Plus{}_r	& \textrm{i}\Re{}	& \Re{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	&  \Re{}	& \textrm{i}\Re{} \\
		\Plus{}_r	& \Im{}		&\textrm{i}\Im{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	& \Im{}		&\textrm{i}\Im{} \\
		\Plus{}_r	&  \Re{}	&\textrm{i}\Re{} \\
	\end{bmatrix}$ \\

@@

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$	&  $0$ \\
		$0$	& $1$	& $0$ \\
		$0$	& $0$	& $1$ \\
	\end{bmatrix}$ 
	$\bf{c}$ \\

@@

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$						&  $0$ \\
		$0$	& \Re{} +\textrm{i}\Im{}	& $0$ \\
		$0$	& $0$						& \Re{} +\textrm{i}\Im{} \\
	\end{bmatrix}$ 
	$\bf{c}$
	\\

	~\citeasnoun{Delaunay1932} does not 
	consider the boundary transformations 
	in detail. 
	However, he uses them to 
	define the process of Selling reduction. 
	For example in \SVI{}, 
	he lists the following as one of the possible results 
	for a transformation on \si{}:
	\SvecA{}.
	The third matrix above 
	(the third boundary transform for $s_1$) 
	implements this operation and interchanges the
	real part of \ciii{} and the imaginary part of \cii{}.

@@

	The considerable regularity 
	of the transformation matrices (above) highlights one
	of the important aspects of Selling reduction 
	as used by~\citeasnoun{Delaunay1932}
	when compared to Niggli reduction~\cite{Niggli1928}. 
	Where all the 	boundaries of the fundamental orthant 
	in \CIII ~and \SVI{} are basically the same 
	(and indeed are related by reflections), 
	the boundaries formed in Niggli reduction are of multiple types, 
	and the fundamental unit of the space representing 
	Niggli reduced cells (\GVI{}, see~\citeasnoun{Andrews2014}) is non-convex.

	The matrices display one of the properties of \CIII{} 
	that make it a useful representation. 
	For the scalar being transformed, it and its 
	opposite scalar create a unique row in each matrix. 
	Those rows contain
	only the minus operator and zeros, 
	highlighting the unique relationship of that pair of scalars.

	Several aspects of C3 are obvious from inspecting the matrices above. 
	First, we see that each boundary has four possible 
	transformations that can be applied. 
	Because the each of the transformations at boundaries are self-inverse, 
	they are the same transformations that would 
	be used in the process of cell (lattice) reduction. 
	~\citeasnoun{Delaunay1932} and~\citeasnoun{Delone1975} give 
	only two choices. Presumably for simplicity they did not list
	the transformations that used the "exchange" operator 
	(see~\cite{andrews2019b}).

>>>>

	\keyword{lattice}
	\keyword{reduction}
	\keyword{Delone}
	\keyword{Selling}
	\keyword{\CIII}

@@

	In \CIII{}, in terms of the Delone scalars, 
	a vector is \{(\si,\siv ), (\sii,\sv),(\siii,\svi)\}, 
	where the real and imaginary parts
	of each are the ``opposite'' scalars 
	according to the definition of~\citeasnoun{Delaunay1932} (see~\citeasnoun{andrews2019a}).
	As a mnemonic device, 
	note that the complex components involve ($\alpha,a$), ($\beta, b$), and ($\gamma,c$).
	Also consider that each complex term uses all 
	four 3-space vectors; for example, $c_1$ is ($b \cdot c$, $a \cdot d$)

@@

	\begin{table}	
		\label{tab:operators}
		\caption{The Result column values give the products of each operator as applied to $(x_j, y_j)$}.
		\begin{tabular}{c l l l }
			\toprule
			Operator			&Usage						&Result					&Name\\
			\midrule
			$\Minus{}_r $		&  $\Minus{}_r(c_j)$ 		& $(-x_j, -x_j+y_j)$ 	& Minus real \\ 
			$\Minus{}_i $ 		& $\Minus{}_i(c_j)$ 		& $(x_j-y_j,-y_j) $ 	& Minus imag\\ 
			$\textfrak{P}_r$ 	& $ \textfrak{P}_r(c_j)$ 	& $(x_j, x_j)$ 			& Plus real\\ 
			$\textfrak{P}_i$ 	&  $\textfrak{P}_i(c_j)$  	& $(y_j, y_j)$ 			& Plus imag\\ 
			$\Real$ 			&  $\Real(c_j)$ 			& $x_j$ 				& Real \\ 
			$\Imaginary$ 		&  $\Imaginary(c_j)$ 		& $y_j$ 				& Imaginary\\
			\bottomrule
		\end{tabular}		
	\end{table}

@@

	$\begin{bmatrix}
		\Minus{}_r		& 0					& 0 \\
		\Plus{}_r		&  \textrm{i}\Re{}	& \Re{} \\
		\textfrak{P}_r	& \textrm{i}\Im{}	& \Im{}
	\end{bmatrix}$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0 				& 0 \\
		\Plus{}_r	&\textrm{i}\Im{}	& \Im{} \\
		\Plus{}_r	& \textrm{i}\Re{}	& \Re{} \\
	\end{bmatrix}$ 
	%
	$\begin{bmatrix}
		\label{thirdmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	&  \Re{}	& \textrm{i}\Re{} \\
		\Plus{}_r	& \Im{}		&\textrm{i}\Im{}
	\end{bmatrix}	$
	%
	$\begin{bmatrix}
		\Minus{}_r	& 0			& 0 \\
		\Plus{}_r	& \Im{}		&\textrm{i}\Im{} \\
		\Plus{}_r	&  \Re{}	&\textrm{i}\Re{} \\
	\end{bmatrix}$ \\

@@

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$	&  $0$ \\
		$0$	& $1$	& $0$ \\
		$0$	& $0$	& $1$ \\
	\end{bmatrix}$ 
	$\bf{c}$. \\

@@

	$\bf{c'}$  = 
	$\begin{bmatrix}
		$1$	& $0$						&  $0$ \\
		$0$	& \Re{} +\textrm{i}\Im{}	& $0$ \\
		$0$	& $0$						& \Re{} +\textrm{i}\Im{} \\
	\end{bmatrix}$ 
	$\bf{c}$.
	\\

	~\citeasnoun{Delaunay1932} does not 
	consider the boundary transformations 
	in detail. 
	However, he uses them to 
	define the process of Selling reduction. 
	For example in \SVI{}, 
	he lists the following as one of the possible results 
	for a transformation on \si{}:
	\SvecA{}.
	The third boundary transform for $s_1$
	implements this operation and interchanges the
	real part of \ciii{} and the imaginary part of \cii{}:

@@

	The considerable regularity 
	of the transformation matrices (above) highlights one
	of the important aspects of Selling reduction 
	as used by~\citeasnoun{Delaunay1932}
	when compared to Niggli reduction~\cite{Niggli1928}. 
	Where all the 	boundaries of the fundamental orthant 
	\SVI{} (and also \CIII{}) are basically the same 
	(and indeed are related by reflections), 
	the boundaries formed in Niggli reduction are of multiple types, 
	and the fundamental unit of the space representing 
	Niggli reduced cells (\GVI{}, see~\citeasnoun{Andrews2014}) is non-convex.

	The matrices display one of the properties of \CIII{} 
	that make it a useful conceptual representation. 
	For the scalar being transformed, it and its 
	opposite scalar create a unique row in each matrix. 
	Those rows contain
	only the minus operator and zeros, 
	highlighting the unique relationship of that pair of scalars.

	Several aspects of \CIII{} are obvious from inspecting the matrices above. 
	First, we see that each boundary has four possible 
	transformations that can be applied. 
	Because the each of the transformations at boundaries are self-inverse, 
	they are the same transformations that would 
	be used in the process of cell (lattice) reduction. 
	~\citeasnoun{Delaunay1932} and~\citeasnoun{Delone1975} give 
	only two choices. Presumably for simplicity they did not list
	the transformations that used the "exchange" operator 
	(see~\cite{andrews2019b}).
